Hydras \& Co.: Formalized mathematics in Coq\\ for inspiration and entertainment

### 2022-06-22 doc/JFLA2022/Slides/Slides.tex
last changes in Slides ?

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{frame}
  \frametitle{Ordinals: a short reminder}

  \begin{figure}[h]
    \scalebox{0.6}{
  \centering
\fbox{\Large
  \begin{minipage}{0.4\linewidth}
  \begin{align*}
     &\textcolor{blue}{0},\,1,2,3,4,5,6,7,8,9,10,11,12,13,14,15,16,17,\ldots\\
&\textcolor{red}{\omega},\,\omega+1,\omega+2,\omega+3,\ldots\\
&\textcolor{red}{\omega\times 2},\,\omega\times 2+1,\ldots, \textcolor{red}{\omega\times 3},\,\omega\times 3+1,\ldots, \textcolor{red}{\omega\times 4},\ldots\\
&\textcolor{red}{\omega^2},\ldots, \textcolor{red}{\omega^2\times 42},\ldots,\textcolor{red}{\omega^3},\ldots, \textcolor{red}{\omega^4},\omega^4+1,\ldots\\
&\textcolor{red}{\omega^\omega},\ldots, \textcolor{red}{\omega^\omega+\omega^7\times 8},\ldots,\textcolor{red}{\omega^\omega\times 2},\omega^\omega\times 2+1, \ldots\\
&\textcolor{red}{\omega^{\omega^\omega}},\ldots, \textcolor{red}{\omega^{\omega^\omega}+\omega^\omega\times 42+ \omega^{55}+\omega}, \ldots, \textcolor{red}{\omega^{\omega^{\omega+1}}}, \omega^{\omega^{\omega+1}}+1,\dots\\
     & \textcolor{red!50}{\epsilon_0 (= \omega^{\epsilon_0)}},
       \textcolor{black!50}{\epsilon_0+1}, \textcolor{black!50}{\epsilon_0+2}, \textcolor{black!50}{\epsilon_0+3}, \ldots\\
& \textcolor{red!50}{\epsilon_1}, \ldots, \textcolor{red!50}{\epsilon_2}, \ldots, \textcolor{red!50}{\epsilon_\omega},\ldots \\
& \textcolor{red!50}{\Gamma_0}, \textcolor{black!50}{\Gamma_0+1}, \textcolor{black!50}{\Gamma_0+2}, \textcolor{black!50}{\Gamma_0+3},\ldots, \textcolor{red!50}{\Gamma_0+\omega}, \ldots\\
&\ldots
  \end{align*}   
  \end{minipage}}}

  \caption{A short overview of the sequence of ordinal numbers}
  \label{fig:ordinal-sequence}
\end{figure}
\end{frame}
